\documentclass {article}
\usepackage{amsmath}
\usepackage{todonotes}

\newcommand\reals{\mathbf{R}}

\newcommand\spline[4]{P(#1, #2, #3, #4)}
\newcommand\splinev[3]{v(#1, #2, #3)}
\newcommand\splinea[2]{\spline{b_{#1}}{c_{#1}}{T_{#1}}{#2}}
\newcommand\splineva[2]{\splinev{c_{#1}}{T_{#1}}{#2}}

\newcommand\dotspline[4]{\dot{P}(#1, #2, #3, #4)}
\newcommand\dotsplinev[3]{\dot{v}(#1, #2, #3)}
\newcommand\dotsplinea[2]{\dotspline{b_{#1}}{c_{#1}}{T_{#1}}{#2}}
\newcommand\dotsplineva[2]{\dotsplinev{c_{#1}}{T_{#1}}{#2}}

\newcommand\subspline[5]{P^{#1}(#2, #3, #4, #5)}
\newcommand\subsplinea[3]{\subspline{#1}{b_{#2}}{c_{#2}}{T_{#2}}{#3}}

\newcommand\Jplusq[2]{\frac{\partial\oplus}{\partial{q}}(#1,#2)}
\newcommand\Jplusv[2]{\frac{\partial\oplus}{\partial{v}}(#1,#2)}
\newcommand\Jminusl[2]{\frac{\partial\ominus}{\partial{q_l}}(#1,#2)}
\newcommand\Jminusr[2]{\frac{\partial\ominus}{\partial{q_r}}(#1,#2)}

\newcommand\Hplusvv[2]{\frac{\partial^2\oplus}{\partial^2{v}}(#1,#2)}
\newcommand\Hminusrr[2]{\frac{\partial^2\ominus}{\partial^2{q_r}}(#1,#2)}

% \newcommand\constraintIa{}
% \newcommand\constraintIb{}

\begin{document}

\section{Problem statement}
Let $B^n_k(u), 0 \le k \le n, u \in [0,1]$ be a base of the set of polynoms of degree inferior
or equal to $n$. We define:
\begin{equation}
  \spline{b}{c}{T}{t} = b \oplus \splinev{c}{T}{t}
  % \spline{b}{c}{T}{t} = b \oplus \sum_k c_k B^n_k(\frac{t}{T})
  \label{eq:splinedef}
\end{equation}
where $$ \splinev{c}{T}{t} = \sum_k B^n_k(\frac{t}{T}) c^k $$

\subsection{Continuity constraint}

\begin{align}
  \splinea{i}{T_i} &= \splinea{i+1}{0} \label{eq:continuitydef_0i}\\
  q_{initial}      &= \splinea{  0}{0} \label{eq:continuitydef_00} \\
  \splinea{N}{T_N} &= q_{goal}         \label{eq:continuitydef_0N} \\
%
  \dotsplinea{i}{T_i} &= \dotsplinea{i+1}{0} \label{eq:continuitydef_1i} \\
  \dot{q}_{initial}   &= \dotsplinea{  0}{0} \label{eq:continuitydef_10} \\
  \dotsplinea{N}{T_N} &= \dot{q}_{goal}      \label{eq:continuitydef_1N}
  % \label{<++>}
\end{align}

Equations~\eqref{eq:continuitydef_0i} and~\eqref{eq:continuitydef_1i} can be reformulated
as follows\footnote{This relies on the fact that $\Jplusv{q}{v}^{-1} = \Jminusr{q}{q\oplus v}$}.

\begin{align*}
  \splineva{i}{T_i} &= (b_{i+1} \oplus \splineva{i+1}{0}) \ominus b_i \\
  \dotsplineva{i}{T_i} &=
  % \Jplusv{b_i}{\splineva{i}{T_i}}^{-1} \times
  \Jminusr{b_i}{b_i\oplus\splineva{i}{T_i}} \times
  \Jplusv{b_{i+1}}{\splineva{i+1}{0}} \times
  \dotsplineva{i+1}{0}
\end{align*}

\subsubsection{Bezier curves}

We implement continuity constraint as explicit constraints.

\begin{align*}
  \splineva{i+1}{0} &= c_{i+1}^{0} \\
  \splineva{i}{T_i} &= c_{i}^{n}   \\
  \dotsplineva{i+1}{0} &= \frac{n}{T_{i+1}} (c_{i+1}^{1}-c_{i+1}^0) \\
  \dotsplineva{i}{T_i} &= \frac{n}{T_i} (c_i^{n} - c_i^{n-1})
\end{align*}

Thus, for $0 \le i < N$:
\begin{align*}
  c_i^n     &= (b_{i+1} \oplus c_{i+1}^{0}) \ominus b_i \\
  c_i^{n-1} &= c_i^n - \frac{T_i}{T_{i+1}}
  \Jminusr{b_i}{b_i\oplus c_i^n} \times
  \Jplusv{b_{i+1}}{c_{i+1}^0} \times
  (c_{i+1}^{1}-c_{i+1}^0)
\end{align*}

Equations~\eqref{eq:continuitydef_00} and~\eqref{eq:continuitydef_10} becomes:
\begin{align*}
  c_0^0 &= q_{initial} \ominus b_0 \\
  c_0^1 &= c_0^0 + \frac{T_0}{n}
  \Jplusv{b_0}{c_0^0}
  \dot{q}_{initial}
\end{align*}

Equations~\eqref{eq:continuitydef_0N} and~\eqref{eq:continuitydef_1N} becomes:
\begin{align*}
  c_N^n     &= q_{goal} \ominus b_N \\
  c_N^{n-1} &= c_N^n - \frac{T_N}{n}
  \Jminusr{b_N}{b_N\oplus c_N^n} \times
  \dot{q}_{goal}
\end{align*}

\paragraph{Derivatives} for $0 \le i < N$:
\begin{align*}
  \frac{\partial{c_i^n}}{\partial{c^0_{i+1}}} &=
  \Jminusl{b_{i+1} \oplus c_{i+1}^{0}}{b_i} \times
  \Jplusv{b_{i+1}}{c_{i+1}^{0}} \\
%
  \frac{\partial{c_i^{n-1}}}{\partial{c^k_{i+1}}} &=
  \frac{\partial{c_i^n}}{\partial{c^k_{i+1}}} - \frac{T_i}{T_{i+1}}
  % \left(\right.
  \Bigg(
  \\
  % \Jminusr{b_i}{b_i\oplus c_i^n}
  & \bigg[
    \Hminusrr{b_i}{c_i^0}
    \Jplusv{b_i}{c_i^0}
    \frac{\partial{c_i^n}}{\partial{c^k_{i+1}}}
  \bigg]
  \Jplusv{b_{i+1}}{c_{i+1}^0}
  (c_{i+1}^{1}-c_{i+1}^0)
  \\
  + &
  \delta_{0,k}
  \Jminusr{b_i}{b_i\oplus c_i^n}
  % \Jplusv{b_{i+1}}{c_{i+1}^
  \bigg[
    \Hplusvv{b_i}{c_i^0}
    I_r
    % \frac{\partial{c_{i+1}^0}}{\partial{c^k_{i+1}}}
  \bigg]
  (c_{i+1}^{1}-c_{i+1}^0)
  \\
  + &
  (\delta_{1,k} - \delta_{0,k})
  \Jminusr{b_i}{b_i\oplus c_i^n}
  \Jplusv{b_{i+1}}{c_{i+1}^0}
  % (c_{i+1}^{1}-c_{i+1}^0)
  % \left.\right)
  \Bigg)
\end{align*}

\subsubsection{Implementation}
This is implemented in class {\texttt ExplicitContinuityFunction}
in file {\texttt src/path-optimization/spline-gradient-based/continuity.hh}.

Currently, the second order derivatives of the integration and difference operators
($\oplus$ and $\ominus$) are not implemented. The derivative of the continuity constraint is
only correct on vector spaces.

\subsection{Path constraints}

We consider four types of constraints, as follows.
\begin{align}
     \subsplinea{(a)}{i}{t} &= f_i (\subsplinea{(b)}{i}{t}) \label{eq:constraintdef_Ia}
  \\ \subsplinea{(c)}{i}{t} &= \bar{f_i} (\subsplinea{(d)}{i}{t}) \oplus r_i \label{eq:constraintdef_IIa}
  \\      F_i  (\splinea{i}{t}) &= 0   \label{eq:constraintdef_Ib}
  \\ \bar{F_i} (\splinea{i}{t}) &= R_i \label{eq:constraintdef_IIb}
\end{align}

\subsubsection{Implicit constraints}
Equation~\eqref{eq:constraintdef_Ib} becomes, for $0\le i\le N$:
\begin{align*}
  G_i(b_i, c_i, T_i) &= 0 \\
  G_i(b_{i+1}, c_{i+1}, T_{i+1}) &= 0 \\
\end{align*}
where $G_i(b_i, c_i, T_i) = F_i  (\splinea{i}{0})$.

Equation~\eqref{eq:constraintdef_IIb} becomes, for $0\le i\le N$:
\begin{equation*}
  \bar{G_i}(b_i, c_i, T_i, b_{i+1}, c_{i+1}, T_{i+1}) = 0
\end{equation*}
where $
\bar{G_i}(b_i, c_i, T_i, b_{i+1}, c_{i+1}, T_{i+1}) =
\bar{F_i} (\splinea{i}{0}) - \bar{F_i} (\splinea{i+1}{0})
$
and 
$
\bar{G_N}(b_N, c_N, T_N) =
\bar{F_N} (\splinea{N}{0}) - \bar{F_N} (\splinea{N}{T_N})
$

\paragraph{Implementation} of $G_i$ function is done in class {\texttt hpp::constraints::function::Difference}
in {\texttt hpp-constraints} package.

\subsubsection{Explicit constraints}
If $f_i$ in Equation~\eqref{eq:constraintdef_Ia}
is such that $f_i(\subsplinea{(b)}{i}{t})$ is a polynom
of degree inferior or equal to $n$, then
Equation~\eqref{eq:constraintdef_Ia} can be converted into
an explicit constraint such as
$$
b_i^{(a)}, c_i^{(a)}  = g_i (b_i^{(b)}, c_i^{(b)}, T_i)
$$
Otherwise, Equation~\eqref{eq:constraintdef_Ia} becomes
a proxy function.

Consider now Equation~\eqref{eq:constraintdef_IIa}.
As $r_i$ is independant of $t$, it can be one of the expression below.
\begin{align*}
  r^{0-}_i &= \subsplinea{(c)}{i-1}{T_{i-1}} &\ominus& \bar{f_i} (\subsplinea{(d)}{i-1}{T_{i-1}})) \\
  r^{0+}_i &= \subsplinea{(c)}{i  }{      0} &\ominus& \bar{f_i} (\subsplinea{(d)}{i  }{      0})) \\
  r^{1-}_i &= \subsplinea{(c)}{i  }{T_{i  }} &\ominus& \bar{f_i} (\subsplinea{(d)}{i  }{T_{i  }})) \\
  r^{1+}_i &= \subsplinea{(c)}{i+1}{      0} &\ominus& \bar{f_i} (\subsplinea{(d)}{i+1}{      0}))
\end{align*}
In what follows, we choose the expression of $r_i$ which, if possible, keeps the constraint explicit.

If $\bar{f_i}$
is such that $\bar{f_i}(\subsplinea{(b)}{i}{t})\oplus r_i$ is a polynom
of degree inferior or equal to $n$, then
Equation~\eqref{eq:constraintdef_IIa} can be converted into
an explicit constraint such as
$$
b_i^{(c)}, c_i^{(c)}  = \bar{g_i} (b_i^{(d)}, c_i^{(d)}, T_i) \oplus r_i
$$
For instance, this happens when $\bar{f_i}$ is constant (e.g. {\texttt LockedJoint} constraints).

In the general case,
we define it either as a proxy constraint or as an implicit constraint.
For simplicity, we always use the following expression for $r_i$.
$$
  r_i = \subsplinea{(c)}{i-1}{T_{i-1}} \ominus \bar{f_i} (\subsplinea{(d)}{i}{0}))
$$
The proxy function is then $
\subsplinea{(c)}{i}{t} = \bar{g_i} (b_i^{(d)}, c_i^{(d)}, T_i) \oplus r_i
$

\paragraph{Implementation} of the above proxy function is done in class \texttt{ProxyFunction}
\todo{Not fully implementated yet.}
in file {\texttt src/path-optimization/spline-gradient-based/proxy.hh}.

\subsubsection{Proxy functions}
A proxy function is a function that outputs a subconfiguration for a subpath,
from another subconfiguration and/or subpath.
They are more general than explicit function since the resulting trajectory is not
necessarily a spline.
The proxy function replaces the path value
$ p_i^{(c)}(t) = \subsplinea{(c)}{i}{t} $ by
$$ p_i^{(c)}(t) \gets Proxy (b_j^{(d)}, c_j^{(d)}, T_j, t) $$

$(i,(c))$ is the output subset. $(j,(d))$ is the input subset.

Any constraint that depends on $(i, (c))$ will be converted into
a function that depends on $(j, (d))$ using the chaining rule.

The output subset should be removed from the variables,
e.g. by adding an explicit constant constraint on them.
Corresponding continuity constraints should be removed
if ensured by other means or made implicit.

\paragraph{Implementation} of functions using proxies is done in class
\texttt{ProxiedFunction} \todo{Not implemented yet}
in file {\texttt src/path-optimization/spline-gradient-based/proxy.hh}.

\section{Resolution using quadratic programming}

\section{Resolution using non-linear optimization}

\end{document}
